\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-11 syntactic-example.tex
Save, Working on example.

>>>>

\begin{minted}{Coq}
  (* First Note that how inductive type is written in our format
     we use 1, 0 to indicate unit type and bottom type *)
  Inductive N :=
    | O : 1 -> (0 -> N) -> N 
    | S : 1 -> (1 -> N) -> N
  (* For example, Number 1 is encoded using
      1 = S () (fun _ -> O () (fun x -> x is ⊥)) *)

Family A.
  Inductive N := O : N. 
  Family handler.
    O : self[A].N * self[A].N 
      := (self[A].O, self[A].O).
  EndFamily.
  pred : self[A].N -> self[A].N * self[A].N 
    := (* handler as recursor *) .
  k := self[A].pred self[A].O
EndFamily.

Family A2 extends A.
  Extend Inductive N := S : N -> N.
  Extend Family handler.
    Inherit O.
    S : N*N -> N*N 
      := fun (x,y) => (y, self[A2].S y).
  EndFamily.
  pred : self[A].N -> self[A].N * self[A].N 
    := (* .. Override ..  *) .
  Inherits k
EndFamily.
\end{minted}

\begin{align*}
  "Osig" &:= \goodWSig{\cdot}{w+ \ \top \ \bot \  w\cdot}{1} \\
  "sig"_1 &:= \goodSig{\cdot}{\nu^+ \ \nu\cdot  \ (\bW \ "Osig"[\pi_1])}{1}  \\
  "obj"_1 &:= \goodTerm{\cdot}{\mu^+ \ \mu\cdot \ {id_s} \ *}{\cL"sig"_1}\\
  \cC"sig"_1 &= \goodType{\cdot}{\Sigma \ \top \ (\bW \ "Osig"[\pi_1]) }{} \\
  "sig"_2 &:=  \goodSig{\cdot}{\nu^+ \ "sig"_1 \ {id_s} \ El ("W" ("pjr" \ \pi_2))}{2} \\ 
  "O" &:= {"Wsup" \ ("pjr" \pi_2) \ () \ ("elim-"\bot \ \pi_2)}  \\ 
  & \text{ and thus }  \goodTerm{\cdot, \cC"sig"_1}{"O"}{El ("W" ("pjr" \pi_2))} \\
  "obj"_2 &:= \goodTerm{\cdot}{\mu^+ \ "obj"_1 \ "O"}{\cL"sig"_2} \\
  "sig"_2' &:= \goodType{\cdot}{\Sigma (\Sigma \top \cU)El ("pjr" \pi_2)}{} \\ 
  \cC"sig"_2 &= \goodType{\cdot}{\Sigma (\Sigma \top (\bW \ "Osig"[\pi_1]))El \ W("pjr" \pi_2) }{} \\ 
  "sl"_1 &:= ((*, "W" ("pjr" ("pjl" \pi_2)) ), "pjr" \pi_2) \\ 
  & \text{ and thus }  \goodSeal{\cdot}{"sl"_1}{"sig"_2}{"sig"_2'} \\
  "pN"_1 &:= \goodType{\cdot, "sig"_2'}{El ("pjr" ("pjl" \pi_2)) * El ("pjr" ("pjl" \pi_2))}{} \\
  "handler"_1 & := \goodTerm{\cdot, "sig"_2'}{\_}{\cL(\nu^+ \ \nu\cdot \ \{id_s\} "pN"_1)} \\
  "sig"_3 &:= \goodSig{\cdot}{\nu^+ "sig"_2 \{"sl"_1\} \ \cL(\nu^+ \ \nu\cdot \ \{id_s\} "pN"_1)}{3} \\ 
  "predT" := (\Pi & \ El ("W"("pjr" ("pjl" ("pjl" \pi_2)))) \\  
  & (El ("W" ("pjr" ("pjl" ("pjl" \pi_2))))[\pi_1])) \\
  "pred"_1 & := \goodTerm{\cdot, \cC "sig"_3}{\lambda ("Wrec" \_)}{predT} \\ 
  "sig"_4 &:= \nu^+ \ "sig"_3 \ \{id_s\} \ "predT" \\ 
  "sl"_4 &:= \goodSeal{\cdot}{\_}{"sig"_4}{"sig"_4'} \\ 
  "pN"_2 &:= \goodType{\cdot, "sig"_4'}{El ("pjr" ("pjl" \pi_2)) * El ("pjr" ("pjl" \pi_2))}{} \\
  "sig"_5 &:= \nu^+ \ "sig"_4 \ \{"sl"_4\} \  "pN"_2 \\ 
  "Nsig" &:= \goodWSig{\cdot}{w+ \ \top \ \bot \  "Osig"}{1} \\ 
  "sig"_{11} &:= \goodSig{\cdot}{\nu^+ \ \nu\cdot  \ (\bW \ "Nsig"[\pi_1])}{1} \\
  "inh"_1 &:= \goodInh{\cdot}{"inhid"}{"sig"_1}{"sig"_{11}}\\
  "O"' &:= {"Wsup" \ ("pjr" \pi_2) \ () \ ("elim-"\bot \ \pi_2)}  \\ 
  & \text{ but }  \goodTerm{\cdot, \cC"sig"_{11}}{"O"'}{El ("W" ("pjr" \pi_2))} \\
  "sig"_{21} &:= \nu^+ \ "sig"_{11} \ \{id_s\} (El (W (pjr p₂))) \\ 
  "inh"_2 &:= \goodInh{\cdot}{"inhov" \ "inh"_1 \ "O"'}{"sig"_2}{"sig"_{21}}\\
  "predT"' := (\Pi & \ El ("W"("pjr"  ("pjl" \pi_2))) \\  
  & (El ("W" ("pjr" ("pjl"  \pi_2)))[\pi_1])) \\
  "sig"_{22} &:= \nu^+ \ "sig"_{21} \ \{id_s\} \ "predT"' \\ 
  "sig"_{21}' &:= \goodType{\cdot}{\Sigma (\Sigma \top \cU) (El ("pjr" \pi_2))}{} \\
  "sig"_{22}' &:= \goodType{\cdot}{\Sigma "sig"_{21}' (\Pi \ El ("pjr"  ("pjl" \pi_2)) (El  ("pjr" ("pjl"  \pi_2))[\pi_1]))}{} \\
  "sl"_{22} &:= \goodSeal{\cdot}{\_}{"sig"_{22}}{"sig"_{22}'} \\ 
  \uparrow^s &:= \goodTerm{\cdot, "sig"_{22}'}{\_}{"sig"_2'[\pi_1]} \\ 
  "inh"_3 &:= \goodInh{\cdot}{\_}{"sig"_2}{"sig"_{22}} \\ 
  "pN"_3 &:= "pN"_1[(\pi_1, \uparrow^s)] \\ 
  "inh"_{in0} &:= \goodInh{\cdot, "sig"_{22}'}{"inhid"}{(\nu^+ \ \nu\cdot \ ("pN"_1[\pi_1]))[(\pi_1, \uparrow^s)]}{(\nu^+ \cdot ("pN"_3[\pi_1]))} \\
  "inh"_{in} &:= \goodInh{\cdot , "sig"_{22}'}{\_}{(\nu^+ \ \nu\cdot \ "pN"_1[\pi_1])[(\pi_1, \uparrow^s)]}{(\nu^+ \ \cdot \ ("pN"_3[\pi_1]) \ \{id_s\} (\Pi "pN"_3 ("pN"_3[\pi_1])) )[\pi_1]}\\
  "sig"_{31} &:=  \nu^+ \ "sig"_{22} \ {"sl"_{22}}\  \cL(\nu^+ \cdot ("pN"_3[\pi_1])  (\Pi "pN"_3 ("pN"_3[\pi_1]))[\pi_1]) \\ 
  "inh"_4 &:= \goodInh{\cdot}{"inh+inh" \ "inh"_3 \uparrow^s "inh"_{in}}{"sig"_3}{"sig"_{31}} 
\end{align*}
